An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
add algorithm

\begin{algorithm}
%\State Let $\theta$ be the list of possible types for the intermediate representation of interest.
\caption{Probabilistically Learn Rules}
  \begin{algorithmic}[1]
    \State learnRules($C$):\\
    Input: $C$ contains intermediate representations\\ 
     \qquad \enspace \enspace of configuration files\\
    Intermediate Representation of configuration file, $M$, where the $i$-th entry of $M$ is denoted by $M_i$\\
    \For{each file $F$ in $C$}
        \For{each entry $e$ in $F$}
               \If{$g(e)$ is false}
                        \State continue to next entry
               \EndIf
                \For{$\tau \in typelist(e)$}
                        \For{$t \in templates(\tau)$}
                        \If{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
                                        \State update $p_{\tau}$ appropriately
                                \ElsIf{anti($t$) is satisfied over rest of entries}
                                        \State update $p_{\tau}$ appropriately
                                \EndIf
                        %Check if $t$ is satisfied  over rest 
                        \EndFor
               \EndFor
          \EndFor
      \EndFor
  \end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}
\caption{Probabilistically Learn Rules}
  Let $\theta$ be the list of possible types for the intermediate representation of interest.
  \begin{algorithmic}[1]
  \State \textbf{learnRules}($C$):\\

    Input: $C$ contains intermediate representations\\ 
     \qquad \enspace \enspace of configuration files\\

    \For{each file $F$ in $C$}
      \For{each $\tau \in \theta$}
        \State $R = \{\}$
        \State $Q = filter(F,\tau)$ 
        \State // $Q$ contains entries in $F$ with $\tau$ in type list
        \For{each entry $e$ in $Q$}
               \If{$g(e)$ is false}
                        \State continue to next entry
                        \Else \enspace $R = R  \cup  \textrm{constructRules}(e, \tau, Q)$
               \EndIf
                        %Check if $t$ is satisfied  over rest 
        \EndFor
     \State Update $p_{\tau}$ appropriately
     \EndFor
    \EndFor
  \end{algorithmic}
\end{algorithm}

%                \For{$\tau \in typelist(e)$}
%                        \For{$t \in templates(\tau)$}
%                        \If{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
%                                        \State update $p_{\tau}$ appropriately
%                                \ElsIf{anti($t$) is satisfied over rest of entries}
%                                        \State update $p_{\tau}$ appropriately
%                                \EndIf

\begin{algorithm}
\caption{constructRules}
  \begin{algorithmic}[1]
  \State \textbf{constructRules}($e, \tau, Q$):\\
    Input: entry $e$ from intermediate representation\\ 
     \qquad \enspace \enspace type $\tau$\\
     \qquad \enspace \enspace set of entries $Q$\\
     $R = \{\}$
     \For{each $t \in templates(\tau)$}
      \State Let $P$ be the set of permutations of distinct entries from $Q$, with arity of $t$, containing $e$
      \For{each $p \in P$}
%      \State Let an entry in $D$ be represented by $(e, e_1, e_2, \ldots)$
      \State Construct the rule $r$ corresponding to $t(v(e_1), v(e_2), \ldots, v(e), \ldots, v(e_{n-1}), v(e_n))$.
      \If{$r$ is satisfied}
        $R = R \cup r$
      \EndIf
     \EndFor
     \EndFor
     \State return $R$
  \end{algorithmic}
\end{algorithm}
